Create datasets for supplemental analyses

### 2023-05-18 code/translocation_survival_createdata.Rmd
Minor edits and remove unnecessary comments

```{r save-site-data}
translocation_sites %>% write_csv(here::here("data", "raw", "translocation_sites.csv"))
# translocation_sites <- read_csv(here::here("data", "raw", "translocation_sites.csv"))
```

@@

```{r save-frog-characteristics-data}
frog_characteristics %>% write_csv(here::here("data", "raw", "frog_characteristics.csv"))
# frog_characteristics <- read_csv(here::here("data", "raw", "frog_characteristics.csv"))
```

@@

```{r save-frog-captures-data}
frog_captures %>% write_csv(here::here("data", "raw", "frog_captures.csv"))
# frog_captures <- read_csv(here::here("data", "raw", "frog_captures.csv"))
```

@@

```{r save-raw-translocated-frogs-data}
frog_translocation %>% write_csv(here::here("data", "raw", "frog_translocation.csv"))
# frog_translocation <- read_csv(here::here("data", "raw", "frog_translocation.csv"))
```

@@

```{r save-raw-frog-survival-data}
frog_survival %>% write_csv(here::here("data", "raw", "frog_survival.csv"))
# frog_survival <- read_csv(here::here("data", "raw", "frog_survival.csv"))
```

@@

```{r check-sex}
frog_captures %>% distinct(pit_tag_ref, sex) %>% count(pit_tag_ref, sex) %>% filter(n > 1) # make sure that only one sex recorded per tag at recipient site

@@

```{r save_clean_translocation_data}
frog_translocation %>% write_csv(here::here("data", "clean", "frog_translocation_final.csv"))
# frog_translocation <- read_csv(here::here("data", "clean", "frog_translocation_final.csv"))
```

>>>>

```{r save-site-data}
translocation_sites %>% write_csv(here::here("data", "raw", "translocation_sites.csv"))
```

@@

```{r save-frog-characteristics-data}
frog_characteristics %>% write_csv(here::here("data", "raw", "frog_characteristics.csv"))
```

@@

```{r save-frog-captures-data}
frog_captures %>% write_csv(here::here("data", "raw", "frog_captures.csv"))
```

@@

```{r save-raw-translocated-frogs-data}
frog_translocation %>% write_csv(here::here("data", "raw", "frog_translocation.csv"))
```

@@

```{r save-raw-frog-survival-data}
frog_survival %>% write_csv(here::here("data", "raw", "frog_survival.csv"))
```

@@

```{r check-sex}
frog_captures %>% distinct(pit_tag_ref, sex) %>% count(pit_tag_ref, sex) %>% filter(n > 1) # ensure only one sex per tag at recipient site

@@

```{r save_clean_translocation_data}
frog_translocation %>% write_csv(here::here("data", "clean", "frog_translocation_final.csv"))
```

### 2023-05-18 code/translocation_survival_createdata_supp.Rmd
Minor edits and remove unnecessary comments

```{r}
frogsbd <- frogs_all %>% 
  inner_join(bd_add, by = c("visit_date", "pit_tag_ref")) %>% 
  mutate(period = if_else(survey_type == "cmr", "after", "before")) %>% # use 0/1 instead?
  relocate(period, .after = survey_type) %>% 
  arrange(site_id, visit_date)
```

>>>>

```{r}
frogsbd <- frogs_all %>% 
  inner_join(bd_add, by = c("visit_date", "pit_tag_ref")) %>% 
  mutate(period = if_else(survey_type == "cmr", "after", "before")) %>% 
  relocate(period, .after = survey_type) %>% 
  arrange(site_id, visit_date)
```
